Agda Meets Accelerate

### 2012-08-30 paper/main.tex
draft of talk

Given a host languages with an expressive type system, it is
attractive to leverage that type system to express static properties
of the embedded language. For example, Accelerate, an embedded array
language for Haskell, uses Haskell's recent support for type-level
programming like GADTs and type families in that
manner~\cite{ChakravartyKellerLeeMcdonellGrover2011}. This design
choice is important for approaches relying on runtime code generation:
compile-time faults in the embedded language should be avoided because
it corresponds to at application runtime. Moreover, static guaranties
hold the potential to improve the predictability of parallel
performance.

>>>>

Given a host language with an expressive type system, it is
attractive to leverage that type system to express static properties
of the embedded language. For example, Accelerate, an embedded array
language for Haskell, uses Haskell's recent support for type-level
programming like GADTs and type families in that
manner~\cite{ChakravartyKellerLeeMcdonellGrover2011}. This design
choice is important for approaches relying on runtime code generation:
compile-time faults in the embedded language should be avoided because
it corresponds to at application runtime. Moreover, static guaranties
hold the potential to improve the predictability of parallel
performance.
